% !TEX root = trkjet.tex

The jet reconstruction procedure is identical to that used in Ref.~\cite{2019108}.
The \antikt\ algorithm \cite{Cacciari:2008qp, Fastjet} is first run in four-momentum recombination mode, on $\Delta \eta \times \Delta \phi = 0.1\times 0.1$  calorimeter towers with two \antikt\ radius parameter values ($R=$~0.2 and $R=$~0.4).
The energies in the towers are obtained by summing the energies of calorimeter cells at the electromagnetic energy scale.
Then, an iterative procedure is used to estimate the $\eta$-dependent underlying event (UE)  transverse energy density, while excluding the regions populated by jets.
The estimate of the UE contribution is performed on an event-by-event basis.
Furthermore, the background in \pbpb\ collisions is modulated to account for the azimuthal anisotropy in particle production~\cite{ATLAS:2012at}.
The modulation includes the contributions of the second, third, and fourth order azimuthal anisotropy harmonics.
The UE transverse energy is subtracted from calorimeter towers included in the jet and the four-momentum of the jet is updated accordingly.
Then, a jet $\eta$- and \pT-dependent  correction factor to the \ptjet\ derived from the \pp\ MC is applied to correct for the calorimeter energy response~\cite{Aaboud:2017jcu}.
The same calibration factors are applied both in \pp\ and \pbpb\ collisions.
An additional correction based on \textit{in situ} studies of jets recoiling against photons, $Z$ bosons, and jets in other regions of the calorimeter is applied~\cite{ATL-PHYS-PUB-2015-036,2019167}.
The same jet reconstruction procedure without the azimuthal modulation of the UE is also applied to $pp$ collisions.
The UE subtraction in $pp$ collisions removes the pileup contribution to the jet.
In this analysis, jets are required to have \ptjet\ in the 126--316 \GeV\ range, with rapidity  $|\yjet|<$~1.7.
The \ptjet\ cut is chosen so as to exclude the contribution of ``UE jets'' generated by fluctuations in the underlying event, while the rapidity cut is based on the acceptance of the tracking system.	  
To prevent nearby jets from distorting the measurement of \Dptr\ distributions, jets are rejected if there is a neighboring jet with higher \ptjet\ within an angular distance of $\Delta R < 1.0$.
This isolation requirement removes approximately 0.01\% of jets.
Additionally, generator level-jets are reconstructed by applying the \antikt\ algorithm with radius parameter $R=0.4$ to stable final-state particles from MC generators.
These particles are required to have a lifetime of $\tau>0.3\times 10^{-10}$ s and do not include muons, neutrinos, and particles from pile-up activity.

Charged-particle tracks in \pbpb\ collisions are reconstructed from hits in the inner detector using the track reconstruction algorithm that has been optimized for the high hit density in heavy-ion collisions~\cite{Aaboud:2017all}.
Tracks used in this analysis have $|\eta| < 2.5$ and are required to have at least 9 (11) total hits in the pixel and SCT detectors for charged particles with pseudorapidity \mbox{|\etatrk| $\leq$ 1.65 (|\etatrk| > 1.65)}.
At least one hit is required in one of the two innermost pixel layers.
If the track trajectory passes through an active module in the innermost layer, then a hit in this layer is required.
Additionally, a track must have no more than two holes in the pixel and SCT detectors together, where a hole is defined by the absence of a hit predicted by the track trajectory.
All charged-particle tracks used in this analysis are required to have reconstructed transverse momentum $\pttrk > 1.0 $~\GeV.
In order to suppress a contribution from secondary particles\footnote{Primary particles are defined as particles with a mean lifetime $\tau>0.3\times 10^{-10}$ s either directly produced in \pp\ interactions or from subsequent decays of particles with a shorter lifetime.
All other particles are considered to be secondary.}, the distance of closest approach of the track to the primary vertex is required to be less than a value that varies from 0.45~mm at $\pttrk=4$~\GeV\ to 0.2~mm at $\pttrk=20$~\GeV\ in the transverse plane and is less than 1.0~mm in the longitudinal direction.


The efficiency, $\varepsilon$, for reconstructing charged particles in \PbPb\ and \pp\ collisions is determined using the MC samples described above.
It is evaluated as a function of the generator-level primary particle transverse momentum, \pTtrue, and pseudorapidity, \etatrue, by associating tracks to generator-level primary particles~\cite{Aad:2010ah}.
In both collision systems the efficiency increases slowly with \pTtrue\ and is seen to be independent of \ptjet\ in the measurement phase space.
For \pbpb\ collisions, the efficiency for $|\eta| < 0.3$  is $\sim 80\%$ at 1 GeV and rises to $\sim 85\%$ at 10 GeV.
For $1.0 < |\eta| < 2.0$, the efficiency is $\sim 67\%$ to $\sim 72\%$  over the same \pt\ range, with the variation in efficiency between the most central and peripheral \pbpb\ collisions being approximately 3\% in both $\eta$ ranges.
For \pp\ collisions, the efficiency for $|\eta| < 0.3$ is $\sim85\%$ at 1 GeV, and rises to $\sim 88 \%$ at 10 GeV, remaining relatively constant thereafter.
For $1.0 < |\eta| < 2.0$, the efficiency is $\sim 82\%$ to $\sim 86\%$ over the same \pt\ range.
Further details on the tracking efficiency can be found in Ref.~\cite{Aaboud:2017bzv}.

The contribution of reconstructed tracks that cannot be matched to a generated primary particle in the \pp\ MC samples is less than 2\% in the entire \pttrk\ range under study in both \pp\ and \pbpb\ collisions.
This contribution includes fakes and secondaries, where fakes originate from randomly associated hits in the detector layers that do not correspond to the passage of charged particles.
Both these contributions are corrected for as described in the next section.








