% !TEX root = trkjet.tex
%-------------------------------------------------------------------------------
% This file contains the title, author and abstract.
% It also contains all relevant document numbers used by the different cover pages.
%-------------------------------------------------------------------------------

% Title
\AtlasTitle{Measurement of angular and momentum distributions of charged particles within and around jets in \pbpb\ and $pp$ collisions at $\sqrt{s_{\mathrm{NN}}}=$~5.02~\TeV\ with ATLAS at the LHC}

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{0.1}

% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
Studies of the fragmentation of jets into charged particles in heavy-ion collisions can provide information
about
 the mechanism of jet quenching by the hot and dense QCD matter created in such collisions, the quark-gluon plasma. 
This paper presents a measurement of the angular distribution of charged particles around the jet axis in $\sqrt{s_{\mathrm{NN}}}=$~5.02~\TeV\
 Pb+Pb and \textit{pp} collisions, done using the ATLAS detector at the LHC. The measurement is performed for jets reconstructed with the \antikt\ algorithm with radius parameter $R = $~0.4, and is extended to a distance of $r= 0.8$ outside the jet cone. The charged particles in this analysis have transverse momenta in the \mbox{1 GeV--63 GeV} range while jets have a transverse momenta in the \mbox{126 GeV--316 GeV} range and are restricted to have an absolute value of the jet rapidity be less 1.7. Results are presented as a function of \pbpb\ collision centrality and distance from the jet axis for different jet and charged-particle transverse momenta ranges. There is an enhancement in the yields of charged particles with transverse momenta below 4 GeV in Pb+Pb collisions compared to $pp$ collisions. This enhancement increases for larger angular distances from the jet axis, reaches a peak at $r = 0.6$ and decreases thereafter. Charged particles with transverse momenta above 4 GeV show a depletion in Pb+Pb collisions compared to the $pp$ reference. An enhancement of charged particles of all transverse momenta is also observed in the jet core for distances up to $r = 0.05$ from the jet axis. 
}

% Author - this does not work with revtex (add it after \begin{document})
% This has to be commented out for TDR etc.
 \author{The ATLAS Collaboration}

% ATLAS reference code, to help ATLAS members to locate the paper
\AtlasRefCode{ANA-HION-2018-03-PAPER}

% CERN preprint number
% \PreprintIdNumber{CERN-EP-2019-XX}

% ATLAS date - arXiv submission; usually filled in by the Physics Office
 \AtlasDate{\today}

% ATLAS heading - heading at top of title page. Set for TDR etc.
% \AtlasHeading{ATLAS ABC TDR}

% arXiv identifier
% \arXivId{14XX.YYYY}

% HepData record
% \HepDataRecord{ZZZZZZZZ}

% Submission journal and final reference
 \AtlasJournal{Phys.\ Rev.\ C.}
% \AtlasJournalRef{\PLB 789 (2017) 123}
% \AtlasDOI{}

%-------------------------------------------------------------------------------
% The following information is needed for the cover page. The commands are only defined
% if you use the coverpage option in atlasdoc or use the atlascover package
%-------------------------------------------------------------------------------

% List of supporting notes  (leave as null \AtlasCoverSupportingNote{} if you want to skip this option)
 \AtlasCoverSupportingNote{Correlations between jets and charged particles in Pb+Pb Collisions at 5.02 TeV}{https://cds.cern.ch/record/2304504}
% \AtlasCoverSupportingNote{Short title note 2}{https://cds.cern.ch/record/YYYYYYY}
%
% OR (the 2nd option is deprecated, especially for CONF and PUB notes)
%
% Supporting material TWiki page  (leave as null \AtlasCoverTwikiURL{} if you want to skip this option)
% \AtlasCoverTwikiURL{https://twiki.cern.ch/twiki/bin/view/Atlas/WebHome}

% Comment deadline
% \AtlasCoverCommentsDeadline{DD Month 2019}

% Analysis team members - contact editors should no longer be specified
% as there is a generic email list name for the editors
 \AtlasCoverAnalysisTeam{Akshat Puri, Anne Sickles, Martin Rybar}

% Editorial Board Members - indicate the Chair by a (chair) after his/her name
% Give either all members at once (then they appear on one line), or separately
 \AtlasCoverEdBoardMember{Mario Martinez Perez(chair), Iwona Grabowska-Bold, Benjamin Nachman}
% \AtlasCoverEdBoardMember{EdBoard~Chair~(chair)}
% \AtlasCoverEdBoardMember{EB~Member~1}
% \AtlasCoverEdBoardMember{EB~Member~2}
% \AtlasCoverEdBoardMember{EB~Member~3}

% A PUB note has readers and not an EdBoard--give their names here (one line or several entries)
% \AtlasCoverReaderMember{Reader~1, Reader~2}
% \AtlasCoverReaderMember{Reader~1}
% \AtlasCoverEdBoardMember{Reader~2}

% Editors egroup
 \AtlasCoverEgroupEditors{atlas-ana-hion-2018-03-analysis-team@cern.ch}

% EdBoard egroup
 \AtlasCoverEgroupEdBoard{atlas-ana-hion-2018-03-editorial-board@cern.ch}
